% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\topmargin=-0.5in
\setlength{\textheight}{10in} % increase text height to fit on 1-page 

\begin{document} 

\name{NICOLAS S. MILLER\\[9 pt]}
\address{ 730 Stinson Blvd Apt 319 \\   Minneapolis, MN 55413 \\ nicolasmiller@gmail.com \\   612-965-1669}
                                  
\begin{resume}    
 
\section{EXPERIENCE}
   \vspace{-0.05in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Engineer} \>Boston Scientific Corp.     \>3/09 - 5/11\\
                             \>St. Paul, MN
   \end{tabbing}\vspace{-18pt}      % suppress blank line after tabbing
    As a member of the Programmer Software group, performed formal requirements-based design verification testing of medical device 		software. Developed and maintained automated test protocols in Python. Wrote a test infrastructure module in Python to simplify and automate verification of requirements related to patient data storage. Extended and maintained a Python-based tool for automated generation of user interface layout tests from XML requirements. 
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Engineering Intern} \>Seagate Technology \> 5/07 - 12/07 \\
                          \>Bloomington, MN 
   \end{tabbing}\vspace{-18pt}
   	Collaborated with an interdisciplinary engineering team in the Advanced Materials Technology group to develop
   	software tools automating aspects of the design and testing of hard disk drive air bearings. Developed user interfaces
   	in Java Swing. Implemented a map overlay algorithm to visualize the result of the photolithography process used in the production of air bearings. Used CVS to version control source files and documentation. Maintained unit test coverage and engaged in 			      black-box testing.

   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Engineering Intern}  \>Karges-Falconbridge, Inc. \> Summer 2006\\
                          \>St. Paul, MN
   \end{tabbing}\vspace{-18pt}
   		Developed and tested a Windows Mobile application in C\# .NET that provided an interface to a third-party building information 				system for the purpose of scheduling and logging mechanical system maintenance. Designed and 						implemented an asset management database and corresponding web interface using PHP, MySQL and HTML/CSS. Analyzed and generated 				reports on thermodynamic data generated by building HVAC systems.   

\section{RESEARCH}
\vspace{0.1in}
	``Computer-Aided Color Appearance Design: Data Analysis and Visualization" \\
	Undergraduate Thesis, Fall and Spring Semesters 2007-2008 \\
\\
		Developed OpenGL software in C++ to visualize and expose trends in automotive coating color space data. Implemented a shader in GLSL to visualize surface reflection characteristics of metallic paints.

\section{TECHNICAL SKILLS}          
\vspace{0.05in}	
\normalsize{\section{Programming Languages and Technologies}}
\vspace{0.05in} 
		Proficient in Python, Java and C. Exposed to the following in past projects: C++, C\# .NET, Perl, XML, SQL, Bash, PHP, HTML/CSS.
        %         \begin{itemize}
        %         \item Proficient: Python, Java, C
        %        \item Exposed to: C++, C\# .NET, Perl, XML, SQL, Bash
        %         \end{itemize}	  
	     %     \begin{itemize}
	     %     \item Software development life cycle
       %            \item Documentation composition
       %            \item Version control with cvs and subversion 
       %            \end{itemize}

\normalsize{\section{Applications and Operating Systems}}
\vspace{0.05in} 
		- Microsoft Visual Studio, Eclipse, PyDev, AccuRev, CVS, JIRA \\
		- Microsoft Office: Excel, Word, Powerpoint \\
    - Linux, Mac OS X, Windows 
		
%\begin{itemize}
%		\item Microsoft Visual Studio, Eclipse, PyDev, AccuRev, JIRA
%		\item Microsoft Office: Excel, Word, Powerpoint
 %   \item Linux, Mac OS X, Windows
  %                	\end{itemize}       

\section{EDUCATION}
\vspace{0.05in}         
    University of Minnesota, Minneapolis, MN \\
		Bachelor of Computer Engineering, August 2008 \\
		GPA: 3.5/4.0           
		
\end{resume}
\end{document}